---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
The data is a CSV file with 3 columns. NAs are indicated by "NA", and there is a header row.
```{r}
library(ggplot2)
activityData <- read.csv("activity.csv",header=T,na.strings="NA")
```
The date column is converted to a date type.
```{r}
activityData$date <- as.Date(activityData$date)
```


## What is mean total number of steps taken per day?
First we remove any NAs from the data set
```{r}
activityDataNoNA <- na.omit(activityData)
```

The aggregate function is used to get the sum per day. A histogram is created using ggplot2.
```{r}
stepsPerDay <- aggregate(steps ~ date, data=activityDataNoNA, sum)
qplot(stepsPerDay$steps)
```

Finally, calculate the mean and median number of steps per day.
```{r}
meanSteps <- mean(stepsPerDay$steps)
medianSteps <- median(stepsPerDay$steps)
```
The mean number of steps is `r format(meanSteps,nsmall=2,scientific=F)` and the median number of steps is `r medianSteps`.

## What is the average daily activity pattern?
To determine the average daily activity pattern, the number of steps is averaged across all days for each time interval. Again, the assumption is still that NAs are ignored.
```{r}
avgStepsPerInt <- aggregate(steps ~ interval, data=activityDataNoNA, mean)
```
1. Next create the time series plot.
```{r}
ggplot(data=avgStepsPerInt, aes(x=interval, y=steps)) + geom_point() + geom_line() + xlab("Interval") + ylab("Average number of steps")
```
1. Determine the interval with the maximum average number of steps.
```{r}
intervalMax <- avgStepsPerInt$interval[avgStepsPerInt$steps == max(avgStepsPerInt$steps)]
```
The 5-minute interval with the maximum number of steps, on average across all the days in the dataset, is interval `r intervalMax`.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
